\documentclass{my_cv}
\usepackage[skins]{tcolorbox}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{parskip}
\begin{document}
\begin{multicols}{2}[
    \titletext{Ankit}%
        {Devri}%
        {Hno.377/5,Mohan Mikins Sociey,Vasundhara,GZB,UP,201012}%
        {\href{mailto:first.last@mail.com}{vivekdevri@gmail.com}}%
        {+92 7827737229}%
        {\href{https://github.com/AnkitDevri/}{github.com/AnkitDevri}}%
        {\href{https://www.linkedin.com/in/ankitdevri/}{Linkedin.com/in/ankitdevri}}%
        {}
]
\end{multicols}

\section{\faFileText}{SUMMARY}
An aspiring data scientist dealing with Deep learning and Machine Learning.
He is a intermediately skilled in problem solving and competitive programming. Sometimes tends to differ from traditional way of programming to the solve real life problems using modern AI solutions and so is
his passion is in AI and Machine Learning.

\begin{multicols}{2}
\section{\faPencil}{PROJECTS}
    
\projects{Cars Pricing Predictor Web App}%
    {Deployment at : {\href{https://cars-pricing-prediction.herokuapp.com/}{cars-pricing-prediction.herokuapp.com}}}
    {A web app deployed on Heroku, using a WSGI web framework flask with a machine learning regression model trained on dataset from CarDekho. It simply accepts the attributes of car and predicts using deployed model.The model was trained on data provided by Cardekho.com which contained data of about 4000+ cars. Check it out at : {\textbf{\href{https://github.com/AnkitDevri/carPricePrediction}{GitHub}}} 
    }
    {Heroku, Python, Random Forest,Flask,Regression,Jinja2,Machine Learning,scikit-learn}
    \par
    %
\projects{Denosing AutoEncoder}%
    {Check it out at : {\href{https://github.com/AnkitDevri/Denosing-Autoencoder}{GitHub}} 
    }%
    {A Deep Learning model based on CNN Neural Network, trained on MNIST digit and FASHION MNIST dataset.
     Passing a 28 x 28 pixel image through the model will denoise it. Its accuracy on the MNIST dataset is 98 percent while on FASHION MNIST dataset was 85 percent. The model was trained on about 70000 images on each dataset.}%
    {Python,Deep Learning,CNN,Tensorflow,Keras,scikit-learn}
    \par
\projects{Hospital Web app}%
    {Deployment at : {\href{https://hospmanag.herokuapp.com/}{hospmanag.herokuapp.com}}}%
    {A very basic web app for a hospital management system, deployed on heroku usng the Flask Web Framework. }%
    {Python, HTML, CSS, Javascript,Flask,Heroku}
     

    
    
\section{\faList}{SKILLS}

\textbf{Languages:} C++, Python, C, JavaScript, HTML, CSS, Git

\noindent\textbf{Tools:} Tensorflow, NumPy, Pandas, Flask, scikit-learn

\noindent\textbf{Other:} Problem Solving, Competitive Programming , Data science, ML and Deep Learning

\columnbreak

\section{\faPaintBrush}{TECHNICAL CERTIFICATIONS}
\begin{itemize}[noitemsep]
    \item \textbf{Introduction to TensorFlow for Artificial Intelligence, Machine Learning, and Deep Learning} in Jan 2022 provided by DeepLearning.ai. Check it: \textbf{\href{https://www.coursera.org/account/accomplishments/certificate/H8WRJYD4T2BQ}{here}} .
    \par
    \item Letter of Attendance\textbf{ Nvidia GTC 2021} for sessions at the conference in Dec 2021.
    Check it: \textbf{\href{https://drive.google.com/file/d/16Tgme1Sr4KLjh2kWmrEXJBxSxgiaxqPo/view}{here}}
    \par
    \item \textbf{Summer Training} in \textbf{DSA} by Renaissance provided by ProgrammingPathshala.com in July 2021. Check: \textbf{\href{https://drive.google.com/file/d/1mEDQhzi45hriBOnNocF9JVuJe5caTsaX/view}{here}}
    \par
    \item \textbf{Algorithmic Toolbox} by University of California, San Diego in May 2020. check it: \textbf{\href{https://www.coursera.org/account/accomplishments/certificate/7TUG86DARH68}{here}}.
    \par
    \item \textbf{Ethical Hacking Workshop} at IIT Delhi in Rendezvous 2017. Check it: \textbf{\href{https://drive.google.com/file/d/1I0uNqQeMgE7rf2xn4YXI0yu-UilRbEui/view}{here}}
\end{itemize}

\section{\faGraduationCap}{EDUCATION}
    
\school{Lovely Professional University, Phagwara} %
{From 2019 to 2023} %
{B.Tech in Computer Science and Engineering}
    
\school{St. Teresa School, Indirapuram} %
{From 2007 to 2019} %
{Senior Secondary Education, Board: CBSE }

\section{\faStar}{OTHER CERTIFICATIONS}

\begin{itemize}[noitemsep]
    \item Certificate of Merit for being first in TechnOlympics 2017, in Future Tech Category.
    check it: \textbf{\href{https://drive.google.com/file/d/1RLxo1emzGHALReSLDn7UjfB2_2hTYwOW/view}{here}}
    \item Certification of Commitment at 73rd Repulic Day by Ministry of Defence. Check it: \textbf{\href{https://drive.google.com/file/d/19l8o8HjbIlwEPfwosTMTENgxJ1geFbsB/view?usp=sharing}{here}}
    \item Certification of Participation, by Ministry of Tourism and MyGov. Check it: \textbf{\href{https://drive.google.com/file/d/10gOOfH7SBqizZOaP-F6VMnyDdtaQRh1v/view?usp=sharing}{here}}
\end{itemize}

\section{\faSoccerBallO}{ACTIVITIES / INTERESTS}
Problem solving is daily part of life.
Proactive about learning diverse things and new Technologies.
Interested in new computing technologies in both hardware and software industry.
Playing PC Games like Valorant.
\end{multicols}
\end{document}
